---
title: "NYC Restaurant Inspections"
output: 
  html_document:
    toc: true
    toc_float: true
---

#### Load packages and data

```{r library, message =  FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)

data("rest_inspec")
```

The original dataset is too big, so I am restricting my dataset to inspection that was conducted in 2017 and exclude those observations that don't belong to any borough.
```{r restrict dataset, message = FALSE}
nyc_inspection = 
  rest_inspec %>% 
  janitor::clean_names() %>% 
  filter(inspection_date >= '2017-01-01',
         boro != "Missing") %>% 
  rename(borough = boro) %>% 
  mutate(borough = str_to_title(borough))
```

Three questions I can answer using this dataset:

1. In each borough, how many restaurants were inspected in 2017?
```{r Q1}
nyc_inspection %>%
  filter(grade == "A") %>% 
  group_by(borough) %>% 
  summarize(n_restaurant = n()) %>% 
  mutate(borough = fct_reorder(borough, n_restaurant)) %>% 
  plot_ly(
    x = ~borough, y = ~n_restaurant, color = ~borough,
    type = "bar") %>% 
  layout(title = 'Which borough has the most number of restaurant that received grade A in 2017?', 
         plot_bgcolor = "#e5ecf6", 
         xaxis = list(title = 'Borough'), 
         yaxis = list(title = 'Number of restaurant'), 
         legend = list(title = list(text = 'Borough')))
```


2. Among the inspected restaurant in each borough, what proportion of them received grade A for their inspections?
```{r Q2}
nyc_inspection %>%
  filter(grade == "A") %>% 
  group_by(cuisine_description) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n)) %>%
  slice(1:10) %>% 
  plot_ly(
    labels = ~cuisine_description,
    values = ~n,
    type = 'pie') %>%
  layout(
    title = "Top 10 cuisine in NYC that received grade A in 2017 inspection",
    xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
    yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
    legend = list(title = list(text = 'Type of cuisine')))
```


3. What is the top 10 most common violation code among the inspected restaurants in 2017?
```{r}
nyc_inspection %>% 
  count(violation_code) %>% 
  arrange(desc(n)) %>% 
  slice(1:10)
```

